Learning constraints in tabular data

### 2016-05-17 Paper/ECAI/tabular.tex
start of new intro section 4, have to go now

\newcommand{\tcl}{Tabular Constraint Learning}
%\newcommand{\ctl}{Condensed Tabular Constraint Learning}
\section{Approach to Tabular Constraint Learning}\label{sec:approach}
This section describes our approach to \tcl. The main method takes \textit{groups} and {\template}s as input, and is described in Section~\ref{sec:algo}. We first explain how tables and groups can be extracted from raw spreadsheet data.

>>>>

\newcommand{\tcl}{Tabular Constraint Learning}
%\newcommand{\ctl}{Condensed Tabular Constraint Learning}
\section{Approach to Tabular Constraint Learning}\label{sec:approach}
The aim of our method is to detect constraints between rows and columns of tabular data. Recall that a valid argument assignment for a constraint is an assignment of each argument of the constraint to a block, such that the constraint, that is, its signature and definition, is satisfied.
\tias{I here use constraint and constraint template interchangeably}

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into type-consistent contiguous \textit{superblocks}
\item Generate for each constraint all valid argument assignments:
\begin{enumerate}
\item For each constraint, generate all candidate \textit{super-assignments} by selecting compatible superblocks for each argument
\item For each candidate super-assignment, generate all valid argument assignments from the superblocks.
\end{enumerate}
\end{enumerate}

The core of our method is step 3. In principle, one could use a generate-and-test approach by generating all possible blocks from the superblock and testing each combination of blocks for each of the arguments of the constraints. However, this ... \textit{blows up} ...

Hence, we divide this step into two parts: in the first part, we will reason over entire superblocks by generating all possible combinations of superblocks that...

\paragraph{Rest old text}

This section describes our approach to \tcl. The main method takes \textit{groups} and {\template}s as input, and is described in Section~\ref{sec:algo}. We first explain how tables and groups can be extracted from raw spreadsheet data.
